Calibrating the pixel-level Kepler imaging data with a causal data-driven model \\

### 2016-02-23 documents/ms/ms.tex
revise caption of figures and fix a paragraph in discussion

\begin{abstract}
Astronomical observations are affected by several kinds of noise, each with its own causal source; 
there is photon noise, stochastic source variability, and residuals coming from imperfect calibration of the detector or telescope. 
The precision of NASA \Kepler\ photometry for exoplanet science---% no spaces around ---
the most precise photometric measurements of stars ever made---%
appears to be limited by unknown or untracked variations in spacecraft pointing and temperature, 
and unmodeled stellar variability. Here we present the Causal Pixel Model (\name) for \Kepler\ data, 
a data-driven model intended to capture variability but preserve transit signals. 
The \name\ works at the pixel level so that
it can capture very fine-grained information about the variation of the spacecraft.
\remove{The \name\ predicts each target pixel value from a large number of pixels of other stars sharing the instrument variabilities 
while not containing any information on possible transits in the target star.} \revise{The CPM models the systematic effects in the time series of a pixel using the pixels
of many other stars and the assumption that any shared signal in
these causally disconnected light curves is caused by instrumental
effects.} In addition, we use the target star's future and past (auto-regression). 
By appropriately separating, for each data point, the data into training and test sets, 
  we ensure that information about any transit will be perfectly isolated from the model. 
The method has four \remove{hyper-parameters (the number of predictor stars, the auto-regressive window size, 
and two L2-regularization amplitudes for model components),}
\revise{tuning parameters---the number of predictor stars or pixels, the auto-regressive window size, 
and two L2-regularization amplitudes for model components,}
 which we set by cross-validation. 
We determine  \remove{a generic set ofhyper-parameters}\revise{values for tuning parameters} that works well for most of the stars and apply the method to a corresponding set of target stars.
\remove{We find that we can consistently outperform (for the purposes of exoplanet detection) 
  the \Kepler\ Pre-search Data Conditioning (PDC) method for exoplanet discovery.} 
\revise{We find that \name\ can consistently produce low-noise light-curves. In this paper, we demonstrate that pixel-level de-trending is possible while retaining transit signals and we think that methods like \name\ are generally applicable and might be useful for  K2, TESS, etc, where the data aren't clean postage stamps like \Kepler.}

@@

In general, there are many reasons for apparent photometric variability in a \Kepler\ source.
There is intrinsic stellar variability,
  which is of interest to some and a nuisance to others.
There is also variability of overlapping fainter stars;
  that is, confusion noise combined with variability of the confusing sources.
There are small changes in spacecraft pointing,
  which leads to slightly different illumination of the focal-plane pixels,
  and thus different sensitivity to variations in the device.
There are also \emph{intra-pixel} sensitivity variations that can contribute\revise{(\citealt{subpixel})}.
There are small changes in spacecraft temperature,
  which lead to point-spread function (PSF) and differential \remove{(across the focal plane)} pointing changes.
These also lead to changes in pixel and intra-pixel illumination.
Stellar proper motion, geometric parallaxes, and differential stellar aberration as the spacecraft orbits all do more of the same.
There is electronic cross-talk between detectors and charge-transfer inefficiency;
  these can effectively transfer variability from one source to another.
There are additional electronics effects like ``rolling bands'' that put additional features into light-curves \revise{\citep{handbook}}.
There are also \remove{probably} changes to the detector sensitivity with temperature and time,
  possibly illimination-history effects,
  and possibly other sources of variability not yet considered.
The remarkable thing about \Kepler\ is that it is trying to measure stars at a level of precision
  much higher than ever previously attempted;
  new effects really \emph{must} appear at some point.
In \figurename~\ref{ccd}, we show the pixel-level variability in the \Kepler\ data
  near one bright star that shows minimal intrinsic variability;
  this figure highlights the spacecraft-induced effects.

\remove{We propose and advise dealing with}\revise{We propose to mitigate} these variations in \Kepler\ light-curves by \emph{modeling} them.
In this context, a model is \remove{(at least)} a parameterized function that can predict data, given parameter settings,
  and an objective function that can be used to set or sample those parameters.
In some cases, the objective function can be given a probabilistic justification or interpretation, e.g., if it is constructed using a likelihood and a prior pdf.
The model can be a physical model (of the spacecraft PSF, pointing, temperature, and so on)
  or it can be a flexible, effective model that has no direct interpretation in terms of physical spacecraft parameters.
If done well, we would expect a physical model to do a better job,
  because it embodies more prior information,
  but it requires research and intuition about dominant effects. 
If this research and intuition is wrong or incomplete, a physical model may actually perform worse.
The model we propose here is in the non-physical, effective category.
The \Kepler\ community is familiar with these kinds of models;
  to our knowledge, \emph{all} successful light-curve ``de-trending'' methods
  are flexible, effective models.

@@

\revise{In the most recent version of PDC (PDC-MAP, \citealt{pdc2,pdc3}), filtered light-curves of other stars are used. Using a set of relatively quiet stars on each detector, the
top 8 principal components are computed for every quarter of Kepler
data. The maximum a posteriori linear combination of these basis light
curves---computed using an empirical prior on the trend
magnitudes---are used to model and remove the systematics in all the
Kepler light curves. The choice to use such a small number of
components and to apply priors was made in order to reduce
over-fitting and retain physical signals after systematics removal.}

@@

PDC \remove{``de-trends''}\revise{``co-trends'' or calibrates} the \Kepler\ light-curves by removing those parts that are explained by the basis light-curves
  generated from a principal components analysis (PCA) of filtered light-curves.
That is, it exploits statistical dependences between different time series, regularizing the fit (and avoiding over-fitting) 
  by filtering and restricting the dimensionality (through PCA).

The method proposed here, The Causal Pixel Model(\name), shares the motivation of PDC.
The main differences are that
\begin{enumerate}
\item
\name\ works in the pixel domain, not the light-curve domain, so it has access to more fine-grained information
\item
\name\ has far more freedom (far more parameters) than the PDC
  but it strictly avoids over-fitting the light-curves on exoplanet-transit time-scales
  through strong regularization and a train-and-test framework. 
  \revise{PDC mitigates overfitting by
reducing the freedom of the model and applying empirical priors to the
fit coefficients.}
\item 
\name\ directly optimizes for prediction accuracy, while PDC uses PCA projections.
\item
\remove{the purpose of \name\ is to search for exoplanets, so in \name, intrinsic stellar
  variability is also removed as well as the systematics.}
  \revise{The current version of \name\ is
tuned to remove systematics while minimizing the impact on exoplanet
transit signals. It makes no attempt to retain lower frequency signals
that can be produced by other astrophysical signals.}
\item 
\name\ uses as inputs only instantaneous values of other stars, plus near future and past of the star itself in an autoregressive fashion, while PDC works with time series (light-curves) of the other stars.
\end{enumerate}

The two methods (\name\ and PDC) are similar however,
  in that they both make the \remove{(implicit or explicit)} assumption that whatever spacecraft effects are imprinting variability on a stellar light-curve
  must also be imprinting similar or related variability on other light-curves.
\remove{In their current versions, they also assume that the relationships can be captured with linear models (although we have also used nonlinear predictions methods for \name, which would be harder to do in PDC).}
By going to the pixel level (unlike the PDC, which works at the stellar-photometry level),
  \name\ makes it easier for the model to capture variability
  that is coming through variations in the centroids and point-spread function
  from spacecraft pointing, roll, and temperature.

@@

The second general idea about data-driven modelling is the investigator's beliefs about the causal processes that generate the data are crucial in restricting the kinds of data that can be used as input to the model.
That is, different assumptions about the physical properties of the data and the data-taking system lead to different structures for the data-driven model.
In the case of \Kepler\ data, 
  if we examine two arbitrary stars far away from each other 
  on the same CCD as in Fig~\ref{ccd} (every grid in the plot is a pixel light-curve time series), 
  we can obviously see that the two stars that are hundreds pixel away from each other do have similar trends. 
  If we believe that different stars in the \Kepler\ field vary independently 
  (that is, are not physically synchronized in any way) because of the distance between them, 
  then the only reason that one star might show variability that is strongly \emph{predictive} (useful for prediction) of another star's variability
  is that both stars are being observed by the same device or spacecraft.
That is, one star's pixels can be used to predict another star's pixels inasmuch as spacecraft issues imprint on both stars in related ways;
  they share a common cause---the systematics.  
For another example, if we think the spacecraft is being affected by
  processes that take place over time-scales longer than a single read-out
  (for example, thermal processes),
  then it would be sensible to model the data at time $t$ using not just simultaneous data, but also data from a range of times around $t$.
For another example, if an investigator doesn't care about preserving stellar variability,
  and just wants to detect exoplanet transits (say),
  pixels from the target star can be used to predict pixels from the target star,
  provided they are at large-enough time lags that they don't contain information about
  the signals of interest (i.e., the transits).
That is, if the model is designed to fit not just spacecraft variability
  but also intrinsic stellar variability,
  the predictive model will be permitted to use as input pixels that \emph{do} overlap the target star.
In what follows, we are going to use input data both from pixels of other stars and the target star pixels' past and future.
These models ought to remove both spacecraft variability and intrinsic stellar variability, which is \remove{optimal}\revise{optimized} for exoplanet transit searching.

@@

Finally, the fifth general idea is that there is no objective \emph{ground truth} against which we can tell
  that any particular data-driven model is better or worse than any other.
This problem is a problem for \name, and for the \Kepler\ PDC, and any other data-driven calibration models.
One might think that the ``best'' model is the one that predicts data with lowest variance;
  this would be true if all models adhered to the same train-and-test framework, which they don't.
Besides, a model that can predict not just the spacecraft-induced variability,
  but also variability caused by exoplanet transits of interest,
  will effectively over-fit and distort the most important information in the light-curves.
That is, what is considered best for modelling the data depends on the objectives of the user.
For us, who are interested (in the long term) in finding and characterizing Earth analogs,
  the ``best'' data-driven model is the one that produces the most success in finding and characterizing Earth analogs!
What we will show in what follows is that the \name\ photometry does not distort
  artificial exoplanet transit signals injected into real \Kepler\ pixel-level data
  \remove{and promising properties of the \name\ outputs}.
In the end, the value of the \name\ will be demonstrated by the scientific projects it enables.

We also want to emphasis that all the calibration in this paper for \Kepler\ is 
  based on the assumption that the device \remove{is 'self-calibratable'}\revise{can be self-calibrated}, 
  which means all the information we need to calibrate the device are contained in the \remove{device itself 
  (either in} science data \remove{or engineering data)} and no external information, 
  for example, measurements from \revise{any} other device, are needed.
\remove{Description}\revise{Elaboration} of the method in \remove{the}\revise{a} machine learning context can be found in \citealt{icml2015}

@@

Because of the train-and-test framework,  
  we expect the \name\ prediction $S_{n}$ to be a prediction of
  what the star light-curve would have under the influence of the spacecraft but with no exoplanet signal. 
Based on this idea, 
  we can construct the ``\name\ flux'' 
  (where the inverted commas indicate that it is not a flux in the sense that stellar variability is not preserved) 
  to be the relative residual between \name\ prediction and SAP Flux $F_{n}$
\begin{eqnarray}
\delta_{n}&\equiv&\frac{F_{n} - S_{n}}{S_{n}}
\quad .
\end{eqnarray} 
In some sense, it is this relative residual\revise{---}the \name\ flux\revise{---}that contains the exoplanet transit signals we seek. 
That is, a transit creates a negative residual away from the prediction, 
  and the amount of relative residual is just the fraction of the light eclipsed by the planet (the transit depth).

@@

\subsection{Effect on transit signals}
One important feature of \name\ is that we use the train-and-test framework to preserve 
the transit signal. To show how well the train-and-test framework performs, we \remove{make}\revise{perform} the
following experiments on \Kepler\ data shown in Fig~\ref{distortion}:
In the light-curve of \revise{KIC 9822284, simple rectangular box model with different depth (from 100 ppm to 1\%) is injected}\remove{single pixel (1, 2) of KIC 9822284, a 10-hrs fake signal 
with amplitude 1.0005 is inserted. To insert the signal, we simply multiply the light-curve 
by the factor of 1.0005, which makes the little bump in the middle of the SAP light-curve 
(black points in the first panel).} With the distorted light-curve, both \name\ and ``ordinary fitting" are applied to the data. 
\revise{By ``ordinary fitting", we mean fitting with all time points,  in comparison with the \name\, in which for each data point the prediction is made without the data in the excluded region.}  
\remove{In the result, we can see that} Both methods fit the light-curve quite well outside the range of the inserted signal. 
However, \remove{when examine how these two models preserve the signal that we care,} the ``ordinary fitting'' fits out a large portion of the signal, while the \name\ \remove{can} preserves the \remove{whole} original amplitude. 
\remove{Therefore,  by} This simple experiment\remove{, we are able to} shows that the train-and-test framework \remove{used here} is capable \remove{to keep}\revise{of preserving} the transit signal \remove{with a particular time scale}. 
\remove{Also we want to emphasise that it} This is crucial for searching for
exoplanets, especially \remove{the small ones such as} Earth-like planets, which only have \remove{about tens of parts per million}\revise{$\backsim$ 100\ ppm} signals \remove{in the light-curve}. \revise{But there are issues: 
The \name\ does not predict the light-curve very well around the box model, since in these regions the prediction is under the strong influence of the transit signal. 
Thus the \name\ will introduce some distortion around the transit signal, and \revise{we expect that} the distortion increases with the depth of the signal. This issue will be discussed in detail in Section 5.}

\begin{figure}[p]
\begin{center}
\includegraphics[width=0.32\textwidth]{f4a}
\includegraphics[width=0.32\textwidth]{f4b}
\includegraphics[width=0.32\textwidth]{f4c}
\end{center}
\caption{
  \label{distortion} 
  \name\ preserves transit signals.
  \remove{Fake signal with amplitude 1.0005 is inserted into the single pixel (1, 2) of star KIC 9822284.
  In the top panel, the black points shows the SAP flux of the pixel with the injected signal, the bold grey line is the fitting of the SAP flux, and the thin red line is the \name\ prediction.}
  \revise{Simple box models with depth from 100 ppm to 1 percent were injected into the light curve of star KIC 9822284. \emph{Left:} An example of light curve with 500 ppm signal injected. In the top panel, SAP flux is plotted in black, 
    \name\ prediction is in thin red line, 
   ``ordinary fitting'' is in bold grey line.} 
  In the bottom panel, red points and grey cross represent the \name\ flux and the fit flux, while the signal value is indicated by the horizontal line. 
  \name\ largely preserves the signal while the fitting flux overfit the signal.} \revise{But the \name\ flux is distorted a little around the box model. 
  And there is more distortion with a strong signal.
  \emph{Right:} shows the signal depth measured in \name\ and fitting flux relative to the true depth with different box model depth. \name\ can consistently preserve more signal than the "ordinary fitting".}
\end{figure}

\remove{To give a view on how our method performs,}\revise{The} \name\ is applied on several stars with known transit signals but different variability and magnitudes, as shown in Fig.~\ref{fluxes}. 
\remove{From the plots, we can see that}\revise{The} \name\ works \remove{quite} well on these stars, producing \remove{the} \name\ fluxes 
with low variation and preserving the transit signals.
In addition, \name\ and PDC are compared \remove{based}\revise{for} on 6 quiet stars 
(non-variable stars, first two rows of Fig.~\ref{fluxes}). 
The results illustrate that for these quiet stars our approach removes 
\remove{a major part}\revise{the majority} of the variability present in the PDC light-curves, while preserving the transit signals. 
To provide a quantitative comparison, we ran \name\ on 1000 stars from the whole Kepler input catalog 
(500 chosen randomly from the whole list, and 500 random G-type sun-like stars), 
and estimated the Combined Differential Photometric Precision (CDPP,  \citealt{cdpp1} )for the \name\ and PDC.  
CDPP is an estimate of the relative precision in a time window, 
indicating the noise level seen by a transit signal with a given duration. 
\revise{In this paper, the CDPP is calculated by using the equations 6-8 in section 3.3 of \citealt{cdpp1}. The CDPP of both PDC and \name\ is estimated with the same algorithm.} 
The duration is typically chosen to be 3, 6, or 12 hours. 
We use the 12-hour CDPP metric, since the transit duration of an earth-like planet is roughly 10 hours. 
Before the CDPP is estimated, the variability of the stars \remove{are}\revise{is} evaluated by median differential variability 
  (MDV, see \citealt{basri2013} for details). 
Based on the variability, the 100 most variable stars in the list are removed, 
  since PDC is not designed to remove stellar variability, 
  and we want to compare \name\ and PDC on the \remove{close}\revise{same} footing.
Fig.~\ref{cdpp} presents our CDPP comparison of \name\ and PDC, 
  \remove{showing that our method (\name) outperforms PDC.}\revise{4 quarters' (quarter 5, 6, 7, 8. Data of quarter 5 are from Kepler data release 21 and other data are from Kepler data release 24---the current version) data are used to show that \name\ has a consistent performance over a whole orbital period of the Kepler photometer (372 days). We also want to emphasize that both \name\ and PDC are presented here, but since PDC is designed to preserve stellar variability, it is not fair to put \name\ and PDC into competition. The CDPP comparison is made only to give a relative reference how \name\ can perform according to PDC, the Kepler ``gold standard"}

@@

\begin{figure}[p]
\begin{center}
\includegraphics[width=0.32\textwidth]{f5a}
\hfill
\includegraphics[width=0.32\textwidth]{f5e}
\hfill
\includegraphics[width=0.32\textwidth]{f5f}

\includegraphics[width=0.32\textwidth]{f5g}
\hfill
\includegraphics[width=0.32\textwidth]{f5h}
\hfill
\includegraphics[width=0.32\textwidth]{f5i}

\includegraphics[width=0.32\textwidth]{f5j}
\hfill
\includegraphics[width=0.32\textwidth]{f5k}
\hfill
\includegraphics[width=0.32\textwidth]{f5l}
\end{center}

>>>>

\begin{abstract}
Astronomical observations are affected by several kinds of noise, each with its own causal source; 
there is photon noise, stochastic source variability, and residuals coming from imperfect calibration of the detector or telescope. 
The precision of NASA \Kepler\ photometry for exoplanet science---% no spaces around ---
the most precise photometric measurements of stars ever made---%
appears to be limited by unknown or untracked variations in spacecraft pointing and temperature, 
and unmodeled stellar variability. Here we present the Causal Pixel Model (\name) for \Kepler\ data, 
a data-driven model intended to capture variability but preserve transit signals. 
The \name\ works at the pixel level so that
it can capture very fine-grained information about the variation of the spacecraft.
\remove{The \name\ predicts each target pixel value from a large number of pixels of other stars sharing the instrument variabilities 
while not containing any information on possible transits in the target star.} \revise{The CPM models the systematic effects in the time series of a pixel using the pixels
of many other stars and the assumption that any shared signal in
these causally disconnected light curves is caused by instrumental
effects.} In addition, we use the target star's future and past (auto-regression). 
By appropriately separating, for each data point, the data into training and test sets, 
  we ensure that information about any transit will be perfectly isolated from the model. 
The method has four \remove{hyper-parameters (the number of predictor stars, the auto-regressive window size, 
and two L2-regularization amplitudes for model components),}
\revise{tuning parameters---the number of predictor stars or pixels, the auto-regressive window size, 
and two L2-regularization amplitudes for model components,}
 which we set by cross-validation. 
We determine  \remove{a generic set ofhyper-parameters}\revise{values for tuning parameters} that works well for most of the stars and apply the method to a corresponding set of target stars.
\remove{We find that we can consistently outperform (for the purposes of exoplanet detection) 
  the \Kepler\ Pre-search Data Conditioning (PDC) method for exoplanet discovery.} 
\revise{We find that \name\ can consistently produce low-noise light curves. In this paper, we demonstrate that pixel-level de-trending is possible while retaining transit signals and we think that methods like \name\ are generally applicable and might be useful for  K2, TESS, etc, where the data aren't clean postage stamps like \Kepler.}

@@

In general, there are many reasons for apparent photometric variability in a \Kepler\ source.
There is intrinsic stellar variability,
  which is of interest to some and a nuisance to others.
There is also variability of overlapping fainter stars;
  that is, confusion noise combined with variability of the confusing sources.
There are small changes in spacecraft pointing,
  which leads to slightly different illumination of the focal-plane pixels,
  and thus different sensitivity to variations in the device.
There are also \emph{intra-pixel} sensitivity variations that can contribute\revise{(\citealt{subpixel})}.
There are small changes in spacecraft temperature,
  which lead to point-spread function (PSF) and differential \remove{(across the focal plane)} pointing changes.
These also lead to changes in pixel and intra-pixel illumination.
Stellar proper motion, geometric parallaxes, and differential stellar aberration as the spacecraft orbits all do more of the same.
There is electronic cross-talk between detectors and charge-transfer inefficiency;
  these can effectively transfer variability from one source to another.
There are additional electronics effects like ``rolling bands'' that put additional features into light curves \revise{\citep{handbook}}.
There are also \remove{probably} changes to the detector sensitivity with temperature and time,
  possibly illimination-history effects,
  and possibly other sources of variability not yet considered.
The remarkable thing about \Kepler\ is that it is trying to measure stars at a level of precision
  much higher than ever previously attempted;
  new effects really \emph{must} appear at some point.
In \figurename~\ref{ccd}, we show the pixel-level variability in the \Kepler\ data
  near one bright star that shows minimal intrinsic variability;
  this figure highlights the spacecraft-induced effects.

\remove{We propose and advise dealing with}\revise{We propose to mitigate} these variations in \Kepler\ light curves by \emph{modeling} them.
In this context, a model is \remove{(at least)} a parameterized function that can predict data, given parameter settings,
  and an objective function that can be used to set or sample those parameters.
In some cases, the objective function can be given a probabilistic justification or interpretation, e.g., if it is constructed using a likelihood and a prior pdf.
The model can be a physical model (of the spacecraft PSF, pointing, temperature, and so on)
  or it can be a flexible, effective model that has no direct interpretation in terms of physical spacecraft parameters.
If done well, we would expect a physical model to do a better job,
  because it embodies more prior information,
  but it requires research and intuition about dominant effects. 
If this research and intuition is wrong or incomplete, a physical model may actually perform worse.
The model we propose here is in the non-physical, effective category.
The \Kepler\ community is familiar with these kinds of models; to our knowledge, \emph{all} successful light curve ``de-trending'' methods are flexible, effective models.

@@

\revise{In the most recent version of PDC (PDC-MAP, \citealt{pdc2,pdc3}), filtered light curves of other stars are used. Using a set of relatively quiet stars on each detector, the
top 8 principal components are computed for every quarter of Kepler
data. The maximum a posteriori linear combination of these basis light
curves---computed using an empirical prior on the trend
magnitudes---are used to model and remove the systematics in all the
Kepler light curves. The choice to use such a small number of
components and to apply priors was made in order to reduce
over-fitting and retain physical signals after systematics removal.}

@@

PDC \remove{``de-trends''}\revise{``co-trends'' or calibrates} the \Kepler\ light curves by removing those parts that are explained by the basis light curves generated from a principal components analysis (PCA) of filtered light curves.
That is, it exploits statistical dependences between different time series, regularizing the fit (and avoiding over-fitting) 
  by filtering and restricting the dimensionality (through PCA).

The method proposed here, The Causal Pixel Model(\name), shares the motivation of PDC.
The main differences are that
\begin{enumerate}
\item
\name\ works in the pixel domain, not the light curve domain, so it has access to more fine-grained information
\item
\name\ has far more freedom (far more parameters) than the PDC
  but it strictly avoids over-fitting the light curves on exoplanet-transit time-scales
  through strong regularization and a train-and-test framework. 
  \revise{PDC mitigates overfitting by
reducing the freedom of the model and applying empirical priors to the
fit coefficients.}
\item 
\name\ directly optimizes for prediction accuracy, while PDC uses PCA projections.
\item
\remove{the purpose of \name\ is to search for exoplanets, so in \name, intrinsic stellar
  variability is also removed as well as the systematics.}
  \revise{The current version of \name\ is
tuned to remove systematics while minimizing the impact on exoplanet
transit signals. It makes no attempt to retain lower frequency signals
that can be produced by other astrophysical signals.}
\item 
\name\ uses as inputs only instantaneous values of other stars, plus near future and past of the star itself in an autoregressive fashion, while PDC works with time series (light curves) of the other stars.
\end{enumerate}

The two methods (\name\ and PDC) are similar however,
  in that they both make the \remove{(implicit or explicit)} assumption that whatever spacecraft effects are imprinting variability on a stellar light curve must also be imprinting similar or related variability on other light curves.
\remove{In their current versions, they also assume that the relationships can be captured with linear models (although we have also used nonlinear predictions methods for \name, which would be harder to do in PDC).}
By going to the pixel level (unlike the PDC, which works at the stellar-photometry level), \name\ makes it easier for the model to capture variability that is coming through variations in the centroids and point-spread function from spacecraft pointing, roll, and temperature.

@@

The second general idea about data-driven modelling is the investigator's beliefs about the causal processes that generate the data are crucial in restricting the kinds of data that can be used as input to the model.
That is, different assumptions about the physical properties of the data and the data-taking system lead to different structures for the data-driven model.
In the case of \Kepler\ data, if we examine two arbitrary stars far away from each other on the same CCD as in Fig~\ref{ccd} (every grid in the plot is a pixel light curve time series), we can obviously see that the two stars that are hundreds pixel away from each other do have similar trends. 
  If we believe that different stars in the \Kepler\ field vary independently 
  (that is, are not physically synchronized in any way) because of the distance between them, 
  then the only reason that one star might show variability that is strongly \emph{predictive} (useful for prediction) of another star's variability
  is that both stars are being observed by the same device or spacecraft.
That is, one star's pixels can be used to predict another star's pixels inasmuch as spacecraft issues imprint on both stars in related ways;
  they share a common cause---the systematics.  
For another example, if we think the spacecraft is being affected by
  processes that take place over time-scales longer than a single read-out
  (for example, thermal processes),
  then it would be sensible to model the data at time $t$ using not just simultaneous data, but also data from a range of times around $t$.
For another example, if an investigator doesn't care about preserving stellar variability,
  and just wants to detect exoplanet transits (say),
  pixels from the target star can be used to predict pixels from the target star,
  provided they are at large-enough time lags that they don't contain information about
  the signals of interest (i.e., the transits).
That is, if the model is designed to fit not just spacecraft variability
  but also intrinsic stellar variability,
  the predictive model will be permitted to use as input pixels that \emph{do} overlap the target star.
In what follows, we are going to use input data both from pixels of other stars and the target star pixels' past and future.
These models ought to remove both spacecraft variability and intrinsic stellar variability, which is \remove{optimal}\revise{optimized} for exoplanet transit searching.

@@

Finally, the fifth general idea is that there is no objective \emph{ground truth} against which we can tell
  that any particular data-driven model is better or worse than any other.
This problem is a problem for \name, and for the \Kepler\ PDC, and any other data-driven calibration models.
One might think that the ``best'' model is the one that predicts data with lowest variance;
  this would be true if all models adhered to the same train-and-test framework, which they don't.
Besides, a model that can predict not just the spacecraft-induced variability,
  but also variability caused by exoplanet transits of interest, will effectively over-fit and distort the most important information in the light curves.
That is, what is considered best for modelling the data depends on the objectives of the user.
For us, who are interested (in the long term) in finding and characterizing Earth analogs,
  the ``best'' data-driven model is the one that produces the most success in finding and characterizing Earth analogs!
What we will show in what follows is that the \name\ photometry does not distort
  artificial exoplanet transit signals injected into real \Kepler\ pixel-level data
  \remove{and promising properties of the \name\ outputs}.
In the end, the value of the \name\ will be demonstrated by the scientific projects it enables.

We also want to emphasis that all the calibration in this paper for \Kepler\ is 
  based on the assumption that the device \remove{is 'self-calibratable'}\revise{can be self-calibrated}, 
  which means all the information we need to calibrate the device are contained in the \remove{device itself 
  (either in} science data \remove{or engineering data)} and no external information, 
  for example, measurements from \revise{any} other device, are needed.
\remove{Description}\revise{Elaboration} of the method in \remove{the}\revise{a} machine learning context can be found in \citealt{icml2015}.

@@

Because of the train-and-test framework,  we expect the \name\ prediction $S_{n}$ to be a prediction of what the star \remove{light-curve}\revise{light curve} would have under the influence of the spacecraft but with no exoplanet signal. 
Based on this idea, 
  we can construct the ``\name\ flux'' 
  (where the inverted commas indicate that it is not a flux in the sense that stellar variability is not preserved) 
  to be the relative residual between \name\ prediction and SAP Flux $F_{n}$
\begin{eqnarray}
\delta_{n}&\equiv&\frac{F_{n} - S_{n}}{S_{n}}
\quad .
\end{eqnarray} 
In some sense, it is this relative residual\revise{---}the \name\ flux\revise{---}that contains the exoplanet transit signals we seek. 
That is, a transit creates a negative residual away from the prediction, 
  and the amount of relative residual is just the fraction of the light eclipsed by the planet (the transit depth).

@@

\subsection{Effect on transit signals}
One important feature of \name\ is that we use the train-and-test framework to preserve 
the transit signal. To show how well the train-and-test framework performs, we \remove{make}\revise{perform} the
following experiments on \Kepler\ data shown in Fig~\ref{distortion}:
In the light curve of \revise{KIC 9822284, simple rectangular box model with different amplitude (from 100 ppm to 1\%) is injected. To do the injection, each pixel light curve of the target star is multiplied by a factor of the amplitude within a timescale of 8 hours.}\remove{single pixel (1, 2) of KIC 9822284, a 10-hrs fake signal 
with amplitude 1.0005 is inserted. To insert the signal, we simply multiply the light-curve 
by the factor of 1.0005, which makes the little bump in the middle of the SAP light-curve 
(black points in the first panel).} With the distorted light curve, both \name\ and ``ordinary fitting" are applied to the data. 
\revise{By ``ordinary fitting", we mean fitting with all time points,  in comparison with the \name\, in which for each data point the prediction is made without the data in the excluded region.}  
\remove{In the result, we can see that} Both methods fit the light curve quite well outside the range of the inserted signal. 
However, \remove{when examine how these two models preserve the signal that we care,} the ``ordinary fitting'' fits out a large portion of the signal, while the \name\ \remove{can} preserves the \remove{whole} original amplitude. 
\remove{Therefore,  by} This simple experiment\remove{, we are able to} shows that the train-and-test framework \remove{used here} is capable \remove{to keep}\revise{of preserving} the transit signal \remove{with a particular time scale}. 
\remove{Also we want to emphasise that it} This is crucial for searching for
exoplanets, especially \remove{the small ones such as} Earth-like planets, which only have \remove{about tens of parts per million}\revise{$\backsim$ 100\ ppm} signals \remove{in the light-curve}. \revise{But there are issues: 
The \name\ does not predict the light curve very well around the box model, since in these regions the prediction is under the strong influence of the transit signal. 
Thus the \name\ will introduce some distortion around the transit signal, and \revise{we expect that} the distortion increases with the depth of the signal. This issue will be discussed in detail in Section 5.}

\begin{figure}[p]
\begin{center}
\includegraphics[width=0.325\textwidth]{f4a}
\includegraphics[width=0.325\textwidth]{f4b}
\includegraphics[width=0.325\textwidth]{f4c}
\end{center}
\caption{
  \label{distortion} 
  \name\ preserves transit signals.
  \remove{Fake signal with amplitude 1.0005 is inserted into the single pixel (1, 2) of star KIC 9822284.
  In the top panel, the black points shows the SAP flux of the pixel with the injected signal, the bold grey line is the fitting of the SAP flux, and the thin red line is the \name\ prediction.}
  \revise{Simple box models with amplitude from 100 ppm to 1 percent were injected into the light curve of star KIC 9822284. 
  \emph{Left:} An example of light curve with 500 ppm signal injected. In the top panel, SAP flux is plotted in black dots, the \name\ prediction is in thin red line, ``ordinary fitting'' is in bold grey line.}
  In the bottom panel, red points and grey cross represent the \name\ flux and the ``ordinary fitting'' flux, while the signal amplitude is indicated by the horizontal line. 
  \name\ preserves the original signal amplitude while the ``ordinary fitting'' overfits the signal. \revise{But the \name\ flux is distorted a little around the edge of the box model.
  \emph{Middle:} The same plot for light curve with 3000 ppm signal injected. There is more distortion with a stronger signal.
  \emph{Right:} The relative signal amplitude measured in \name\ and ``ordinary fitting'' flux is plotted as a function of the injected signal amplitude. The \name\ can consistently preserve more signal than the ``ordinary fitting".}}
\end{figure}

\remove{To give a view on how our method performs,}\revise{The} \name\ is applied on several stars with known transit signals but different variability and magnitudes, as shown in Fig.~\ref{fluxes}. 
\remove{From the plots, we can see that}\revise{The} \name\ works \remove{quite} well on these stars, producing \remove{the} \name\ fluxes 
with low variation and preserving the transit signals.
In addition, \name\ and PDC are compared \remove{based}\revise{for} on 6 quiet stars 
(non-variable stars, first two rows of Fig.~\ref{fluxes}). 
The results illustrate that for these quiet stars our approach removes 
\remove{a major part}\revise{the majority} of the variability present in the PDC light curves, while preserving the transit signals. 
To provide a quantitative comparison, we ran \name\ on 1000 stars from the whole Kepler input catalog 
(500 chosen randomly from the whole list, and 500 random G-type sun-like stars), 
and estimated the Combined Differential Photometric Precision (CDPP,  \citealt{cdpp1} )for the \name\ and PDC.  
CDPP is an estimate of the relative precision in a time window, 
indicating the noise level seen by a transit signal with a given duration. 
\revise{In this paper, the CDPP is calculated by using the equations 6-8 in section 3.3 of \citealt{cdpp1}. The CDPP of both PDC and \name\ is estimated with the same algorithm.} 
The duration is typically chosen to be 3, 6, or 12 hours. 
We use the 12-hour CDPP metric, since the transit duration of an earth-like planet is roughly 10 hours. 
Before the CDPP is estimated, the variability of the stars \remove{are}\revise{is} evaluated by median differential variability 
  (MDV, see \citealt{basri2013} for details). 
Based on the variability, the 100 most variable stars in the list are removed, 
  since PDC is not designed to remove stellar variability, 
  and we want to compare \name\ and PDC on the \remove{close}\revise{same} footing.
Fig.~\ref{cdpp} presents our CDPP comparison of \name\ and PDC, 
  \remove{showing that our method (\name) outperforms PDC.}\revise{4 quarters' (quarter 5, 6, 7, 8. Data of quarter 5 are from Kepler data release 21 and other data are from Kepler data release 24---the current version) data are used to show that \name\ has a consistent performance over a whole orbital period of the Kepler photometer (372 days). We also want to emphasize that both \name\ and PDC are presented here, but since PDC is designed to preserve stellar variability, it is not fair to put \name\ and PDC into competition. The CDPP comparison is made only to give a relative reference how \name\ can perform according to PDC, the Kepler ``gold standard"}

@@

\begin{figure}[p]
\begin{center}
\includegraphics[width=0.32\textwidth]{f5a}
\hfill
\includegraphics[width=0.32\textwidth]{f5b}
\hfill
\includegraphics[width=0.32\textwidth]{f5c}

\includegraphics[width=0.32\textwidth]{f5d}
\hfill
\includegraphics[width=0.32\textwidth]{f5e}
\hfill
\includegraphics[width=0.32\textwidth]{f5f}

\includegraphics[width=0.32\textwidth]{f5g}
\hfill
\includegraphics[width=0.32\textwidth]{f5h}
\hfill
\includegraphics[width=0.32\textwidth]{f5i}
\end{center}
